Understanding the role of different proxy selection methods in High-Dimensional Propensity Score Framework - A Plasmode simulation study

### 2024-09-11 Writeup/manuscript.Rmd
add some comment to the writeup

@@

The comparison between the data generation process and the analysis process reveals two key differences: (i) The data generation used transformed laboratory variables, whereas the analysis was conducted using only the original laboratory variables. (ii) The data generation employed a simple sum of selected proxy variables (sum of 94 proxy covariates), while the analysis included all proxy variables (143 binary proxies), with 49 of these acting as noise variables. These differences help us assess how the proxy variable selection methods handle model misspecification and the presence of noise variables.

>>>>

\textcolor{blue}{*!!!!!!!! need to write what hdps is, and why alternatives are considered*}

@@

The comparison between the data generation process and the analysis process reveals two key differences: (i) The data generation used transformed laboratory variables, whereas the analysis was conducted using only the original laboratory variables. (ii) The data generation employed a simple sum of selected proxy variables (sum of 94 proxy covariates), while the analysis included all proxy variables (143 \textcolor{green}{bold}{*142*} binary proxies), with 49 \textcolor{green}{bold}{*49? 48?*} of these acting as noise variables. These differences help us assess how the proxy variable selection methods handle model misspecification and the presence of noise variables.
